### 2023-09-05 accepted/COPSolver/manuscript.tex
rewriting the paper introduction

\noindent
\textbf{Abstract}\\
This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has a application of the Fraga's exact method for solving the multi-product batch processing time maximization problem. This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
\vskip0.5cm

@@

%\begin{table}[!h]
\noindent
\begin{tabular}{|l|p{6.5cm}|p{9.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & COPSolver\_1.0-1 \\
\hline
C2 & Permanent link to code/repository used for this code version & \underline{$https://github.com/tbfraga/COPSolver$} \\
\hline
C3  & Permanent link to Reproducible Capsule & \underline{$https://codeocean.com/capsule/4837209$}\\
\hline
C4 & Legal Code License   & Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International Public License \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & c++, CodeBlocks, LINGO, Ubuntu 22.04.1, GitHub\\
\hline
C7 & Compilation requirements, operating environments \& dependencies & elementary OS (can be adapted to Ubuntu) \\
\hline
C8 & If available Link to developer documentation/manual & \underline{$http://tbfraga.github.io/COPSolver/documentation/$} \\
\hline
C9 & Support email for questions & tbfraga@proton.me\\
\hline
\end{tabular}\\
%\caption{Code metadata (mandatory)}
%\label{} 
%\end{table}
\vskip0.5cm
\noindent

@@

The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al. (2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions. The exact analytical method of Fraga et al. (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.

@@

COPSolver is open source software written in C++ language. Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp). Each library will be developed to define and solve a single distinct type of problem. All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively. Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed. Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions. Functions with similar purposes will be named with the same name using the functionalities of polymorphism. The libraries will be distinguished by a distinct namespace containing an acronym that identifies the problem addressed in the library itself. The definition of the problems instances can be done in three distinct ways: 1) through the data.txt file; 2) using solver predefined problems; and 3) generating a problem statically or randomly through pre-established functions of the solver. The config.txt file should be adjusted in order to: 1) inform the type of problem addressed; 2) select the method of defining the problem and the parameters that should be adjusted according to the chosen method; and 3) select the method for solving the problem. In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method. For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results. Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src. The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.

>>>>

\noindent
\textbf{Abstract}\\
This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has a application of Fraga's exact method for solving the multi-product batch processing time maximization problem. This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
\vskip0.5cm

@@

%\begin{table}[!h]
\noindent
\begin{tabular}{|l|p{6.5cm}|p{9.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & COPSolver\_1.0-1 \\
\hline
C2 & Permanent link to code/repository used for this code version & $https://github.com/tbfraga/COPSolver/releases/tag$ $/v1.0\textrm{-}1$ \\
\hline
C3  & Permanent link to Reproducible Capsule & $https://codeocean.com/capsule/4837209$\\
\hline
C4 & Legal Code License   & Creative Commons Attribution-NonCommercial-NoDerivatives 4.0 International Public License \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & c++, CodeBlocks, LINGO, Ubuntu 22.04.1, GitHub\\
\hline
C7 & Compilation requirements, operating environments \& dependencies & elementary OS (can be adapted to Ubuntu) \\
\hline
C8 & If available Link to developer documentation/manual & \underline{$http://tbfraga.github.io/COPSolver/documentation/$} \\
\hline
C9 & Support email for questions & tbfraga@proton.me\\
\hline
\end{tabular}\\
%\caption{Code metadata (mandatory)}
%\label{} 
%\end{table}
\vskip0.5cm
\noindent

@@

The first version of the software, COPSolver\_1.0-1, applies the exact solution method developed by Fraga et al. (2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions. The exact method of Fraga et al. (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.

@@

COPSolver is an open source software written in C++ language. Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp). Each library will be developed to define and solve a single distinct type of problem. All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively. Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed. Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions. Functions with similar purposes will be named with the same name using the functionalities of polymorphism. The libraries will be distinguished by a distinct namespace containing an acronym that identifies the problem addressed in the library itself. The definition of the problems instances can be done in three distinct ways: 1) through the data.txt file; 2) using solver predefined problems; and 3) generating a problem statically or randomly through pre-established functions of the solver. The config.txt file should be adjusted in order to: 1) inform the type of problem addressed; 2) select the method of defining the problem and the parameters that should be adjusted according to the chosen method; and 3) select the method for solving the problem. In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method. For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results. Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src. The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.
